Appendix S1: Supporting Information

### 2021-08-20 ms/SI.Rmd
Update reference processing
Combine other references and main_library before filtering
Add references to SI

---
bibliography:
  - `r here::here("ms/references.yaml")`
  - `r here::here("ms/references_other.yaml")`
---

@@

**`r s_figure("sampling-curve")`**. Species collection curve for the ferns of Japan fit with the `r pack("iNEXT")` package. Grey shading indicates 95% confidence interval (not visible where it does not extend beyond the fitted line). Point indicates observed taxonomic richness (`r observed_data$qD` taxa, 95% confidence interval `r rich_interval` taxa). Taxa include species, subspecies, and varieties, excluding hybrids. Sampling completeness is estimated to be `r est_completeness` (95% confidence interval `r completeness_interval`).

>>>>

---
bibliography: 
  - `r here::here("ms/references.yaml")`
---

@@

**`r s_figure("sampling-curve")`**. Species collection curve for the ferns of Japan fit with the `r pack("iNEXT")` package [@Hsieh2016]. Grey shading indicates 95% confidence interval (not visible where it does not extend beyond the fitted line). Point indicates observed taxonomic richness (`r observed_data$qD` taxa, 95% confidence interval `r rich_interval` taxa). Taxa include species, subspecies, and varieties, excluding hybrids. Sampling completeness is estimated to be `r est_completeness` (95% confidence interval `r completeness_interval`).
